\Large Classifying Vehicles From Automatic Number \\ Plate Recognition Camera Scans

### 2018-01-29 trips.tex
Added a few corrections

\section{Identifying trips in number plate data}

@@

Furthermore, if we consider all valid trips of vehicle \emph{k}:

@@

where, we consider two sightings of vehicle \emph{k} to be different simply if they were observed at two different points in time:

\begin{equation} \label{e.sighting}
t^{k}_{i} \ne t^{k}_{j} \Rightarrow s^{k}_{i} \ne s^{k}_{j} \ , \ i \ne j
\end{equation}

When identifying trips from GPS traces, . It is easy to see that both $\tau$ and $\Tau$ should be functions of the

>>>>

% !TEX root = paper.tex
\section{Trip identification}

@@

Additionally, if we consider all valid trips of vehicle \emph{k}:

@@

where two sightings of vehicle \emph{k} are different simply if they were observed at two different points in time:

\begin{equation} \label{e.sighting.different}
t^{k}_{i} \ne t^{k}_{j} \Rightarrow s^{k}_{i} \ne s^{k}_{j} \ , \ i \ne j
\end{equation}

It is easy to see that both $\tau$ and $\Tau$ should be functions of the
